\documentclass{article}
\usepackage{hyperref}
\usepackage{amsmath,amssymb}

\begin{document}

\section{Main narrative additions}
\begin{itemize}
    \item We introduce a family of effectively symmetric integrators extending the Euclidean RDE/SDE constructions of Shmelev to general parallelizable manifold settings.
    
    \item We identify a natural low-memory formulation of these methods, and show that in the manifold setting it is compute-optimal in the sense of using the minimal number of exponential evaluations.
    
    \item We provide software support in the JAX ecosystem for constructing, testing, and running efficient manifold neural differential equation solvers.
    
    \item A substantial manifold component probably needs some rewrite since it changes technical framing and the experimental narrative of the paper.
\end{itemize}

\section{Experiments}
\begin{enumerate}
    \item \textbf{OU process / practical stochastic benchmark}
    \begin{itemize}
        \item Consider replacing this with rough Bergomi.
        \item This would respond more directly to the reviewers' concerns about practical relevance.
        \item The implementation is already available.
        \item Possible evaluation metric: signature-kernel-based score.
    \end{itemize}

    \item \textbf{High-dimensional GBM}
    \begin{itemize}
        \item Possibly replace this with rough Bergomi as well.
        \item Otherwise, keep this experiment and emphasise the stiff regime clearly.
    \end{itemize}

    \item \textbf{Manifold ODE task}
    \begin{itemize}
        \item Candidate practically motivated task: \url{https://arxiv.org/abs/2506.06780}.
        \item The implementation is already available.
        \item This would help motivate the geometric extension beyond being a purely formal generalisation.
    \end{itemize}

    \item \textbf{Manifold SDE task}
    \begin{itemize}
        \item One candidate is an affine-invariant OU-type It\^o diffusion on $S_d^{++}$:
        \[
        \mathrm dX_t
        =
        \eta\,\log_{X_t}(M)\,\mathrm dt
        +
        \sigma\,X_t^{1/2}\,\mathrm dB_t\,X_t^{1/2},
        \qquad
        X_0 \in S_d^{++}.
        \]
        
        \item This has some motivation from applications in finance.
        
        \item It would also enable a clean comparison against manifold log-ODE approaches, which are much slower.
        
        \item Other possible directions include topological or Riemannian Schr\"odinger bridge tasks, or more general Riemannian diffusion benchmarks.
    \end{itemize}
\end{enumerate}

\section{Rewrite issues}
\begin{itemize}
    \item If the manifold contribution is made central, then the paper may need to be repositioned as a broader geometric integration paper rather than as a lighter revision of the rejected submission.
    
    \item Manifold material may be better framed as a major extension supported by one strong experiment, rather than as the primary narrative.
\end{itemize}

\bibliographystyle{plain}
\bibliography{neurips2026/neurips_references}

\end{document}